Simulating Dwarf Galaxy Evolution with Individual Star Feedback and Chemical Evolution

### 2018-02-09 main.tex
Update on Overleaf.

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, St, Y, and Ba. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significant metal enriched outflows, leading to a low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis.
\end{abstract}

@@

The native smooth particle hydrodynamics (SPH) scheme is incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}. Even more, a given parameterization is not necessarily applicable generally \citep{Revaz2016}, though recent studies have shown great improvements to this end \citep{Escala2017}. Metal mixing efficiencies may also vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) 
%mm in which they are injected to
    that inject metals into 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how one handles sub-grid metal injection and metal mixing schemes can lead to challenges in connecting models to observations and the fundamental physics that drives galaxy evolution. \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.

@@

We seek to produce a complementary approach to studying galactic chemical evolution with a new chemical evolution scheme implemented in the adaptive mesh refinement code \texttt{Enzo} designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback of both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.

Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime. In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This opens an exciting new channel for testing models of galaxy evolution by enabling us to leverage current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.

This paper is the first in a series of papers examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields %mm tables from the
to track yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
%mm implementation 
in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.

@@

\subsubsection{Diffuse  Heating}
\label{sec:diffusive heating}
We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from each of our star particles. Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

@@

\subsubsection{Lyman-Werner Radiation}
\label{sec:LW}
In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rates. Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section. We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.

@@

\section{Galaxy Initial Conditions}
\label{sec:IC}
The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy. Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or $Z \sim 5.4\times10^{-4} Z_{\odot}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}. Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.

@@

\section{Results}
\label{sec:results}
We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms. This occurs 43 Myr after initialization. Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle formed, and the galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation \textit{(list times here)}. In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{ \textbf{need to adjust overlapping labels} Edge-on views of our dwarf galaxy at four different times in its evolution, separated by 100~Myr, beginning with the time at first star formation and ending at 300 Myr. Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections. These gas cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc. These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy. These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk. The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work. 
% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The total gas scale height at various times throughout the simulation.}
\label{fig:scale_height}
\end{figure}

@@

Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300 -- 350~Myr. One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the phase diagram include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average. We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work. \textbf{is last bit on CR heating and SF gas OK?}

@@

Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. \textbf{Do I need to discuss a little further since it is different than previous sims? If so, where should I go with this?}

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is particularly not surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 50 Myr from 300--350~Myr. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The contribution from the metagalactic background falls below the lower vertical axis limit on this plot. Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars. However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.

@@

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time. After the first 20 Myr, supernova driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 40\% by the end of the simulation. Likewise, the CGM metal content is continually decreasing until the end of the simulation time, from loss through the virial radius of the halo. Although the metal content of the ISM is gradually decreasing throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution.
%\textbf{closing sentence}

@@

It is important to understand how metals from each source of stellar yields (stellar winds, AGB star winds, and supernovae) enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport must occur much more rapidly ($\sim 10^2$~Myr) than what is possible assuming transport at the cold gas sound speed ($\sim 1$~Gyr). This suggests either that metals are transported first through a hot phase or are driven through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}. How metal abundances vary in detail within these galaxies, beyond 1D radial profiles, and whether or not abundance distributions depend on the metal species is uncertain. It is even more unclear as to how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.

@@

Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, and close enough to the Milky Way to conduct this experiment. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the rest in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during the simulation no longer reside within the galaxy's disk. At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that
most of the metals that have been produced at these early times will remain outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.

@@

\subsection{Missing Physics}
Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant.These are discussed below.

@@

\subsection{Detailed Stellar Evolution and Binary Stars}
\section{sec:binary stars}
% Although we track individual stars and assign properties to each based on stellar evolution models, these properties are fixed. A more detailed model could follow each star on an interpolated stellar evolution track, which would account for variations in radiation and stellar wind properties in each star over time.

>>>>

\begin{abstract}
We have developed a new model for stellar feedback in order to simulate the chemodynamical evolution of isolated dwarf galaxies at high resolution in the adaptive mesh refinement hydrodynamics code \textsc{Enzo}. For the first time in galaxy scale simulations, we are capable of capturing detailed stellar feedback from individual stars including stellar winds from massive stars and AGB stars, photoelectric heating, Lyman-Werner dissociation, ionizing radiation tracked through an adaptive ray-tracing radiative transfer method, and core collapse and Type Ia supernovae. 
%This star-by-star method allows us to directly account for variations in stellar properties that govern their feedback properties (mass, lifetime, surface temperature, and metallicity).
In addition, we follow the evolution of star-by-star stellar yields for 15 metal tracer species: C, N, O, Na, Mg, Si, S, Ca, Mn, Fe, Ni, As, Sr, Y, and Ba. We describe these methods in detail, including the additional physics used to model a realistic three-phase interstellar medium. We present the first application of these methods on a 500~Myr simulation of an isolated dwarf galaxy with properties similar to a Local Group ultrafaint dwarf galaxy. We demonstrate that our physics and feedback model is capable of producing a dwarf galaxy whose evolution is consistent with observations in both the Kennicutt-Schmidt relationship and extended Schmidt relationship. Effective feedback drives significant metal enriched outflows, leading to low metal retention fractions consistent with observations. Our low-dust content galaxy exhibits a significant H$_2$ mass fraction, formed primarily through gas-phase H$^{-}$ reactions. We end with a discussion on how this work will impact our understanding of galactic chemical evolution on a species-by-species basis.
\end{abstract}

@@

Fully Lagrangian schemes, like native smooth particle hydrodynamics (SPH), are incapable of capturing mixing between chemically inhomogeneous particles, as necessary for chemical evolution. This must be handled through sub-grid models of turbulent metal diffusion \citep[e.g.][]{Shen2010, Shen2013,Brook2014,Su2017a}. Even more, there are many possible sub-grid models that are not applicable in every regime \citep[see ][]{Revaz2016}, though recent studies have shown great improvements in characterizing various methods \citep{Escala2017}. While mixing occurs in Eulerian codes without sub-grid models, numerical diffusion tends to result in over-mixing, requiring very high resolution or additional viscosity to reduce. Molecular diffusion is certainly not resolved in any galaxy-scale simulation with either method, requiring additional sub-grid models; this can be particularly important for understanding the initial pollution of otherwise pristine gas \citep[see ][ and references therein]{PanScannapiecoScalo2013,Sarmento2017}. Moreover, metal mixing efficiencies may vary species-by-species, as suggested by recent work \citep[e.g.][]{Cohen2013, Roederer2014, FrebelNorris2015, Hirai2017, Cote2017}. Mixing behavior is tied critically to the feedback source (stellar winds, supernovae, and possibly more exotic sources) 
%mm in which they are injected to
    that inject metals into 
the ISM with different energies and on different timescales; the observational effect of this is poorly understood, however. The variations in how different methods handle sub-grid metal injection and metal mixing schemes can lead to uncertainties in connecting models to observations and the fundamental physics that drives galaxy evolution. \textbf{Still not sure about this sentence - but I do need a way to cite mentioned papers:} Extending these models to a grid-based code is a valuable and complementary approach towards investigating galactic chemical evolution that has only been done recently \citep{Few2012,Few2014,Vorobyov2015}.

@@

We introduce a new method for studying galactic chemical evolution that follows stars as individual star particles implemented in the adaptive mesh refinement code \texttt{Enzo}, designed for high resolution simulations of isolated galaxies. The relative simplicity of idealized, isolated galaxy evolution simulations allows for a focused, first-principles approach to studying multi-channel feedback mechanisms. We follow recent work using low mass dwarf galaxies as laboratories to study in detail how feedback governs galaxy evolution \citep{Forbes2016,Hu2016,Hu2017}.
%For example, \citet{Forbes2016} found that photoelectric heating can be a significant source of feedback in small galaxies. \citet{Hu2016} and \citet{Hu2017} examined the relative importance of various feedback physics in regulating ISM properties of dwarf galaxies. 
Our work builds upon our current understanding of feedback and galactic chemodynamics while making three notable advancements: 1) direct star-by-star modeling, 2) stellar wind feedback of both massive stars and AGB stars, and 3) using an adaptive ray tracing method to follow stellar ionizing radiation.

Using star-by-star modeling, we are able to capture in more detail the stellar yields from individual stars released over their lifetime. In addition to better capturing how individual metal species enrich the ISM, this allows us to chemically tag individual stars. This opens an exciting new channel for testing models of galaxy evolution by leveraging current and ongoing observations probing the detailed chemical abundances of stars in the Milky Way and Local Group, such as APOGEE and APOGEE2 \citep{APOGEE2010,APOGEE}, the Gaia-ESO survey \citep{Gaia}, and GALAH \citep{GALAH}.

This paper is the first in a series examining in detail the role that the individual components of multi-channel stellar feedback play in galaxy dynamical and chemical evolution. In this paper we introduce a new method of feedback physics and galactic chemical enrichment in the cosmological, hydrodynamics code \texttt{Enzo}. For the first time in galaxy-scale simulations, we model star formation down to particles representing individual stars, while simultaneously capturing stellar feedback through stellar winds, core collapse and Type Ia supernovae, photoelectric heating, and ionizing radiation through ray-tracing radiative transfer. In addition, we couple to a self-consistent set of stellar yields %mm tables from the
to track yields from massive star stellar winds, AGB star winds, and supernovae. We describe each mode of our multi-channel feedback 
%mm implementation 
in detail below, and briefly discuss their implementation in an isolated dwarf galaxy simulation.

@@

\subsubsection{Diffuse  Heating}
\label{sec:diffusive heating}
We include two forms of diffuse heating in our simulations, each tied directly to the non-equilibrium primordial chemistry network in \texttt{Grackle}: 1) the optically thin, uniform metagalactic UV background \citep{HM2012}, and 2) localized photoelectric heating from the far-ultraviolet (FUV, 6 eV $<$ $h\nu$ $<$ 13.6 eV) radiation from each of our star particles. The FUV flux for each star is again obtained from the OSTAR2002 grid by directly integrating over the SEDs for each gridded star. Like the ionizing radiation, we again use an adjusted black body spectrum to compute the flux for stars off of the grid (see Section~\ref{sec:ionizing radiation} and Appendix~\ref{appendix:radiation}). Photoelectric heating can be a dominant heating mechanism in the ISM of the Milky Way \citep{Parravano2003}, and could be significant in regulating star formation in dwarf galaxies \citep{Forbes2016}. However, this conclusion warrants further research as its exact importance in dwarf galaxies relative to other feedback mechanisms is contentious \citep{Hu2016,Hu2017}. Generally, models for photoelectric heating and Lyman-Werner radiation in hydrodynamic simulations of galaxies adopt a constant value or a static, radial profile. Only recently has the localization and time variation of these processes been considered.

@@

\subsubsection{Lyman-Werner Radiation}
\label{sec:LW}
In addition to the Lyman-Werner radiation from the UV background, we account for localized Lyman-Werner flux from each of our stars to compute the total, local H$_2$ dissociation rates. We compute the stellar LW flux again from the OSTAR2002 grid by integrating the SEDs over photon energies from 11.2~eV to 13.6~eV (see Appendix~\ref{appendix:radiation}). Given the local Lyman-Werner flux, the H$_2$ dissociation rate is taken as $k_{\rm diss} = \sigma_{\rm H2} F_{\rm LW}$, where $\sigma_{\rm H2}$ is the H$_2$ dissociation cross section. We account for approximate H$_2$ self-shielding against these sources of Lyman-Werner flux by implementing the Sobolev-like approximation from \citet{Wolcott-Green2011} in \texttt{Grackle}.

@@

\section{Galaxy Initial Conditions}
\label{sec:IC}
The galaxy presented in this work is constructed to be similar to the observed properties of the Local Group dwarf galaxy Leo P \citep{Giovanelli2013,McQuinn2013,McQuinn2015a,McQuinn2015}, although it is not intended to be a matched model to this galaxy. Leo P is gas rich ($M_{\rm gas} > M_{*}$) and low metallicity, with $M_{\rm HI} = 8.1\times 10^{5}$~M$_{\odot}$ and $M_{*} = 5.6^{+0.4}_{-1.9} \times 10^{5}$~M$_{\odot}$ \citep{McQuinn2015a} extending to a radius $r_{\rm HI} = 500$~pc, and with $12 + \rm{log(O/H)} = 7.17 \pm 0.04$ \citep{Skillman2013}, or a metallicity fraction of $Z \sim 5.4\times10^{-4}$, adopting $Z_{\odot} = 0.018$ from \citet{Asplund2009}. Our dwarf galaxy is constructed without an initial background stellar population, with a total gas mass of $1.8 \times 10^{6}$~M$_{\odot}$ (or $M_{\rm HI} = 1.35 \times 10^{6}$~M$_{\odot}$) and $Z = 4.3\times 10^{-4}$, comparable to the average $z = 0$ metallicity from the stellar models computed in \citet{McQuinn2015}.

@@

\section{Results}
\label{sec:results}
We present our initial results here, providing a brief overview of the morphological (Section~\ref{sec:structure}), star formation (Section~\ref{sec:sfr}), ISM (Section~\ref{sec:phase}), radiation field (Section~\ref{sec:ISRF}), outflow (Section~\ref{sec:outflows}), and chemical (Section~\ref{sec:chemical evolution}) properties of our dwarf galaxy during the first 500~Myr after the first star forms. Unless otherwise noted, $t = 0$ is defined as the time at which the first star particle forms, which is 43~Myr after the actual initialization of the simulation. The galaxy disk is defined as the fixed physical region within a cylindrical radius of 600~pc and $|z| < 200$~pc relative to the center of the galaxy. ISM properties are calculated considering only the gas contained within the disk of the galaxy.

@@

We begin by characterizing the morphological properties of our dwarf galaxy, as demonstrated in a series of face-on and edge-on images, presented in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. Each figure gives density weighted projections of number density (first row), temperature slices (second row), \ion{H}{1} column density projections (third row), and H$_2$ column density projections (fourth row), at four different times in the simulation (0, 150, 300, and 500 Myr). In addition, the number density plots show all main sequence stars in the simulation at the given time, represented by individual black points. Towards the end of the simulation time, the half light radius is $390 \pm 21$ pc, where the uncertainty represents the 1$\sigma$ variation in this quantity during the final 20 Myr.

@@

\begin{figure*}
\centering
\includegraphics[width=0.975\linewidth]{multiplot_4x4_x.png}
\caption{Edge-on views of our dwarf galaxy at four different times in its evolution, 0 Myr, 150 Myr, 300 Myr, and 500 Myr. Shown are density weighted projections of number density (top row), temperature slices (second row), and integrated projections giving \ion{H}{1} column density (third row) and H$_2$ column density (fourth row). Each individual main sequence star particle is shown in the number density projections as a single black dot.}
\label{fig:panel_x}
\end{figure*}

@@

Interestingly, there is significant structure well above the gas disk in the form of dense clouds and filamentary features, as seen in the edge-on projections. These cold gas clumps appear to have typical sizes on order of $\sim$ 10 pc, but with lower density tails that can extend up to 100 pc. These consist of both cool, self-gravitating gas clumps that are being pushed out and ablated by the stellar feedback driven winds, and gas that is cooling and condensing in the disk-halo interface of our dwarf galaxy. These clumps have typical velocities on order of a few to tens of kilometers per second, and appear to survive for 10--100 Myr before being fully ablated or re-accreted onto the main body of the gaseous disk. The evolution of these dense clumps in the context of the disk-halo interface in our low mass dwarf galaxy will be examined in a future work. 
% AE (left out): This is exciting given recent \citep[e.g.][]{Zheng2017} and ongoing \citep{Zheng2017HST} observational observational work examining the disk-halo interface in nearby galaxies.

\begin{figure}
\centering
\includegraphics[width=0.975\linewidth]{scale_height}
\caption{The total gas scale height at various times throughout the simulation. These times match the images in Figures~\ref{fig:panel_x} and ~\ref{fig:panel_z}.}
\label{fig:scale_height}
\end{figure}

@@

Figure~\ref{fig:phase} shows the temperature-density phase diagram of all gas within 0.25 R$_{\rm vir}$ of the center of the galaxy, averaged over the time period 300 -- 350~Myr. One can readily identify the two most massive regions of gas in the simulation, a low density, warm phase produced through ionization and supernovae heating, and a cold, high density phase which makes up most of the mass in the galaxy's disk (see Figure~\ref{fig:ISM_evolution}). Several notable features of the phase diagram include: broad ranges of temperature even in quite dense gas, perhaps produced by photoionization and photoelectric heating, a substantial amount of extremely cold gas below 10~K, and the lack of well defined thermal phases due to the complexity of both the heating and cooling in a turbulent medium. We note that we are likely missing important physics, such as cosmic ray heating and ionization, that would prevent the formation of the coldest gas in this diagram (below about 10~K), but we do not expect this to significantly alter our results. The boxed regime in the lower right corner shows our star formation density and temperature threshold. Gas in this regime is rapidly consumed by star formation and subsequent feedback. Given the small size of our dwarf galaxy, the total amount of mass in this regime at any given instant can be small, but does show up in this time average. We will investigate the typical formation and destruction timescales of this dense, star forming gas in future work.

@@

Together, the CNM and molecular phases comprise $\sim 90\%$ of the total ISM mass, with the remaining dominated by the WNM. While the CNM has a negligible volume fraction, the WNM, WIM, and HIM occupy roughly the same volume fraction. However, the frequent fluctuations in the HIM volume fraction mean that the WIM and WNM more consistently dominate the volume of the galaxy. Together, these figures better quantify the general properties observed in the panel plots in Figure~\ref{fig:panel_x} and Figure~\ref{fig:panel_z}. These results are in contrast with those found for the more massive dwarf galaxy in \citet{Hu2016,Hu2017}. In short, they find the mass and volume fraction of the ISM nearly entirely dominated by warm gas (ionized and neutral), with cold gas comprising $\sim$ 10\% of mass, and negligible volume, and hot gas comprising $\sim$ 10\% of the volume, but negligible mass. Our lower mass, lower metallicity galaxy contains more cold gas (by mass fraction) by a large factor, and more hot gas (by volume fraction) by a factor of a few. The driver of these differences, which are likely somewhat related to differences in the dark matter halo potential, will be investigated in future works.

@@

The interstellar radiation field (ISRF) of our galaxy varies dramatically in both space and time, as has been seen previously in works modeling varying radiation fields both as expected from stellar motions in our own galaxy \citep{Parravano2003}, and in models including radiation \citep[e.g.][]{Hu2017}. This is not particularly surprising in our low SFR regime, where there can be large fluctuations over time as individual massive stars form, move about, and evolve. In Figure~\ref{fig:ISRF} we present azimuthally averaged radial profiles of the ISRF in various bands, time averaged over 50 Myr from 300--350~Myr. The top panel shows $G_{\rm o}$, the ISRF flux between 6--13.6~eV normalized to the value in the solar neighborhood of the Milky Way (see Sec.~\ref{sec:diffusive heating}). The contribution from the metagalactic background falls below the lower vertical axis limit on this plot. Interestingly, the averaged profile appears nearly flat for most of the disk, with an increase at higher radii due to more recently formed stars. However, the ISRF varies significantly over time, fluctuating by an order of magnitude or more at any given radius.

@@

These large metal mass loading factors indicate that a majority of the metals produced in our dwarf galaxy are ejected from the disk. This is quantified in the lower panel of Fig.~\ref{fig:metal_evolution}, where we show the mass fraction of metals in the disk, CGM, and outside the virial radius of our galaxy over time. After the first 20 Myr, supernova driven winds rapidly drive out large quantities of metals from the disk and into the galaxy's halo. This continues throughout the simulation, with only $\sim$12\% of produced metals residing in the disk of the galaxy. It only takes 150 Myr for some metals to reach the virial radius of the halo, with a steadily increasing fraction continually leaving the virial radius, or 40\% by the end of the simulation. Likewise, the CGM metal content is continually decreasing until the end of the simulation, from loss through the virial radius of the halo. Although the metal content of the ISM is gradually decreasing throughout the simulation, it seems somewhat steady at $\sim 10\%$ through the final 200~Myr of evolution. See Section~\ref{sec:obs_metals} for further discussion.
%\textbf{closing sentence}

@@

It is important to understand how metals from each source of stellar yields (stellar winds, AGB star winds, and supernovae) enrich the ISM. Observations of more massive dwarf galaxies than those simulated here indicate fairly uniform radial gas-phase metallicity profiles, even beyond the stellar radius \citep[e.g.][]{Werk2011,Belfiore2017}. This requires that metal mixing and transport must occur much more rapidly ($\sim 10^2$~Myr) than what is possible assuming transport at the cold gas sound speed ($\sim 1$~Gyr). This suggests either that metals are transported first through a hot phase or are driven through efficient turbulent mixing within the ISM \citep[e.g.][]{Tassis2008,YangKrumholz2012}. How metal abundances vary in detail within these galaxies, beyond 1D radial profiles, and whether or not abundance distributions depend on the metal species is uncertain. It is even more unclear how metals are transported and distributed within ultrafaint dwarf galaxies, which generally host too few HII regions for a detailed examination.

@@

Leo P, the dwarf galaxy we approximate in our initial conditions, is extremely valuable as a gaseous, star forming low-mass dwarf galaxy, with an observable \ion{H}{2} region, necessary for determining gas phase abundances, and close enough to the Milky Way to conduct this experiment. Leo P retains $\sim$ 5\% $\pm$ 2\% of its metals, $\sim$ 1\% in stars and the remaining in ISM gas \citep{McQuinn2015}. As discussed in Section~\ref{sec:chemical evolution}, roughly 90\% of the tracked metals produced during the simulation no longer reside within the galaxy's disk. At the end of our simulation, we agree with the observations; however, this is an evolving quantity that also depends on how much (if any) subsequent re-accretion of these metals occurs. Although more than half of these metals are expected to eventually re-accrete \citep{Angles-Alcazar2017}, it is still possible that
most of the metals that have been produced at these early times will remain outside the galaxy disk. We will examine the long term, and species-by-species, evolution of the metal retention fraction in future work.

@@

\subsection{Missing Physics}
Although we include detailed physics in our simulations, there remains additional physical processes that may be relevant, these are discussed below.

@@

\subsection{Detailed Stellar Evolution and Binary Stars}
\label{sec:binary stars}
% Although we track individual stars and assign properties to each based on stellar evolution models, these properties are fixed. A more detailed model could follow each star on an interpolated stellar evolution track, which would account for variations in radiation and stellar wind properties in each star over time.
